\section{Introduction}
\label{sec:introduction}

Elite motorsport race engineering involves continuous, time-constrained decision
making under uncertainty. During a single race session an engineering team must
analyse hundreds of telemetry channels, correlate them with environmental
conditions, and produce actionable setup recommendations within minutes.
Traditional toolchains --- spreadsheets, bespoke dashboards, and human expertise
--- do not scale to the volume and velocity of modern telemetry.

Large language models and agentic frameworks have recently demonstrated the ability
to process heterogeneous data streams, retrieve relevant context, and produce
coherent, multi-step plans. However, their adoption in high-stakes engineering
domains is limited by three open problems:

\begin{enumerate}
  \item \textbf{Uncontrolled generation.} LLM outputs lack methodology enforcement.
    Without governance, agents produce inconsistent or unverifiable artefacts.
  \item \textbf{Tool access security.} Agentic systems that call external tools
    introduce new attack surfaces and audit challenges.
  \item \textbf{Reproducibility.} It is difficult to package an LLM-augmented
    workflow so that third parties can verify or extend its results.
\end{enumerate}

This paper presents a KDD-governed agentic architecture that addresses these
challenges in the race engineering domain. The system is structured as fourteen
specialised repositories, each with a defined responsibility, governed by a
shared methodology enforced through structured document definitions, skill
registries, and an observability platform.

Our main contributions are:

\begin{itemize}
  \item A reference architecture for KDD-governed multi-agent systems in
    high-stakes operational domains (\S\ref{sec:architecture}).
  \item A governance model that enforces methodology compliance at generation
    time (\S\ref{sec:kdd-governance}).
  \item A race AI copilot that translates raw telemetry into evidence-grounded
    decision support (\S\ref{sec:copilot}).
  \item A digital twin validation layer that blocks unsafe recommendations
    (\S\ref{sec:digital-twin}).
  \item An experimental evaluation across nine controlled studies with synthetic
    datasets (\S\ref{sec:methodology}).
  \item A fully packaged reproducibility kit enabling independent verification.
\end{itemize}
