\section{System Architecture}
\label{sec:architecture}

The system is organised as fourteen specialised repositories forming a layered
architecture (Figure~\ref{fig:architecture-overview}). Each repository has a
single defined responsibility and communicates with adjacent layers through
declared interfaces.

\subsection{Layered Organisation}

\begin{description}
  \item[\repo{00-kdd-governance}] Defines the methodology, standards, and
    governance artefacts consumed by all other repositories.
  \item[\repo{01-agent-orchestrator}] Houses the primary agentic engine
    responsible for task decomposition, agent routing, and session management.
  \item[\repo{02-mcp-gateway}] Provides secure, audited access to external
    tools via the Model Context Protocol.
  \item[\repo{03-rag-cag-knowledge-layer}] Manages domain knowledge retrieval
    and context augmentation.
  \item[\repo{04-skills-autoskills-registry}] Stores reusable agent capabilities
    and auto-skill generation pipelines.
  \item[\repo{05-documentation-agent}] Produces traceable, structured
    documentation from agent activity.
  \item[\repo{06-kdd-data-pipelines}] Transforms raw telemetry into features,
    patterns, and evidence packets.
  \item[\repo{07-agentic-workflows}] Declares and executes multi-step
    declarative workflows.
  \item[\repo{08-experimentation-lab}] Designs, executes, and archives
    controlled experiments.
  \item[\repo{09-observability-platform}] Provides metrics, distributed tracing,
    and alerting.
  \item[\repo{10-infra-docker}] Delivers reproducible local development
    environments.
  \item[\repo{11-infra-kubernetes}] Manages cloud-native deployment manifests.
  \item[\repo{12-ci-cd-release-engineering}] Automates build, test, and release
    pipelines.
  \item[\repo{13-security-governance-compliance}] Enforces security controls,
    risk management, and compliance policies.
  \item[\repo{14-paper-reproducibility-kit}] Packages the scientific paper and
    all reproducibility artefacts (this repository).
\end{description}

\subsection{Data Flow}

Telemetry from on-bike sensors enters through \repo{06-kdd-data-pipelines},
where it is transformed into structured evidence packets. Packets are indexed
in \repo{03-rag-cag-knowledge-layer} for retrieval by the race AI copilot.
The copilot, orchestrated by \repo{01-agent-orchestrator}, queries the knowledge
layer, calls tools via \repo{02-mcp-gateway}, and produces recommendations that
pass through the digital twin validation layer before reaching the Race Command
Center dashboard.
