\section{Race AI Copilot}
\label{sec:copilot}

The Race AI Copilot is the core reasoning component of the system. It receives
structured evidence packets from the data pipeline, retrieves relevant historical
knowledge, and produces grounded recommendations.

\subsection{Evidence-Grounded Generation}

Unlike a bare LLM prompted with raw telemetry, the copilot operates on
pre-processed evidence packets. Each packet contains:

\begin{itemize}
  \item extracted features (tyre temperature gradient, suspension travel range,
    spin/slip ratio),
  \item anomaly flags with confidence scores,
  \item session context (lap count, fuel load, ambient conditions),
  \item citations to retrieved historical cases.
\end{itemize}

The copilot prompt is structured by the \sdd~mechanism, guaranteeing that every
recommendation includes evidence citations, confidence, uncertainty bounds, and
the governance metadata required by the \kdd~model.

\subsection{Retrieval Strategy}

The copilot uses a hybrid \rag/\cag~strategy:

\begin{itemize}
  \item \rag~retrieves semantically similar historical sessions from the vector
    index,
  \item \cag~injects circuit-specific setup heuristics from the cached knowledge
    layer without re-indexing.
\end{itemize}

\subsection{Output Format}

Each copilot recommendation is a structured JSON document containing the
recommendation text, confidence score, supporting evidence list, uncertainty
range, and provenance metadata. This format is consumed directly by the \rcc~
dashboard and stored in the audit log.
