\section{Threats to Validity}
\label{sec:threats-to-validity}

\subsection{Internal Validity}

\textbf{Synthetic datasets.} All experiments use synthetically generated
telemetry. Real MotoGP telemetry is subject to commercial confidentiality
agreements. The synthetic generator (\texttt{scripts/generate-synthetic-telemetry.py})
reproduces the statistical structure of typical session data but does not capture
all sources of real-world variance.

\textbf{Single implementation.} Results reflect one instantiation of the proposed
architecture. Alternative implementation choices (different LLM providers, vector
databases, orchestration frameworks) may yield different quantitative outcomes.

\subsection{External Validity}

\textbf{Domain specificity.} The architecture targets elite motorcycle racing.
Transfer to other motorsport disciplines or high-stakes engineering domains would
require adaptation of the domain-specific components (telemetry schema, twin
models, knowledge base structure).

\textbf{Scale.} Experiments simulate single-session scenarios. Production deployment
involves multiple concurrent sessions, larger knowledge bases, and real-time
constraints not captured in the experimental protocol.

\subsection{Construct Validity}

\textbf{Metric definitions.} Traceability score, groundedness, and audit coverage
are operationally defined for this study. Alternative definitions may produce
different baseline/variant gaps.

\textbf{Evaluator reliability.} Evidence quality scores in E06 were assigned by
the authors. Independent blind evaluation would strengthen construct validity.

\subsection{Conclusion Validity}

\textbf{Small sample size.} Ten runs per condition provides sufficient power for
large effect sizes but may miss moderate effects. Future work should expand to
at least thirty independent runs.
